NEED TITLE

### 2014-09-25 ms.tex
Added figures, continued discussion of numerical results

To initialize our simulation, we begin by applying solenoidal stirring forces to the uniform, periodic simulation volume at the root grid resolution of $128^3$ until statistical equilibrium is reached (approximately three crossing times).  After this equilibrium is established, we then apply self gravity, adaptive mesh refinement, and sink particle creation.  In Figure \ref{fig:entire projection} we show a projection along the x-axis of the entire simulation volume that has up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. Regions that are highly refined are the densest regions which are smoother than the low-density more pixelated regions.

@@

These simulations display much more complicated dynamics than is captured by the simple analytic theory of Murray and Chang 2014.  In spite of this, we compare radially averaged profiles around these high density points to their analytic theory.  In fig

@@

What plots should we show?
-density vs r
-velocities vs r
-angular momentum vs r
-mass vs r
-mdot vs r

\begin{figure}
\plotone{frame0241.png}
\caption{Projection along the x-axis of the entire simulation volume. The root grid is $128^3$ with up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. This snapshot is taken at ??. \label{fig:entire projection}}
\end{figure}

\begin{figure}
\plotone{mass.png}
\end{figure}

\begin{figure}
\plotone{Track_0256_000_rho.png}
\caption{Density as a function of radial position from maximum density point.  The density reaches a maximum of $10^6$ times mean density at $r \approx 10^{-3}$ pc and decline to approximately mean density at $r\approx 3$ pc.  The three straight solid lines are $r^{-3/2}$, $r^{-2}$, and $r^{-5/2}$ power laws. }
\end{figure}

\begin{figure}
\plotone{Track_0132_000_rho.png}
\caption{Density as a function of radial position from maximum density point.  The density reaches a maximum of $10^7$ times mean density at $r \approx 10^{-3}$ pc and decline to approximately mean density at $r\approx 3$ pc, a }
\end{figure}

>>>>

To initialize our simulation, we begin by applying solenoidal stirring forces to the uniform, periodic simulation volume at the root grid resolution of $128^3$ until statistical equilibrium is reached (approximately three crossing times).  After this equilibrium is established, we then apply self gravity, adaptive mesh refinement, and sink particle creation.  In Figure \ref{fig:entire projection} we show a projection along the x-axis of the entire simulation volume that has up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. Regions that are highly refined are the densest regions which are smoother than the low-density more pixelated regions.
\begin{figure}
\plotone{frame0241.png}
\caption{Projection along the x-axis of the entire simulation volume. The root grid is $128^3$ with up to 10 levels of refinement, giving an effective resolution of $128\,{\rm K}^3$. This snapshot is taken at ??. \label{fig:entire projection}}
\end{figure}

@@

These simulations display much more complicated dynamics than is captured by the simple analytic theory of Murray and Chang 2014.  In spite of this, we compare radially averaged profiles around these high density points to their analytic theory.  In the left panel of Figure \ref{fig:good_rho_example}, we show the radial density profile around one such high density point. As this figure shows, the radial density profile follows a $r^{-3/2}$ power law in agreement with analytic expections.  This power-law breaks down at small radii, but this is not unexpected as this radii corresponds to the presents of a rotationally support disk.  Such good agreement is not universal for all high density points as shown in the right panel of Figure \ref{fig:bad_rho_example}.  Here the radial density profile follows a $r^{-2}$ power law.  
\begin{figure*}
\plottwo{Track_0256_000_rho.png}{Track_0132_000_rho.png}
\caption{Density as a function of radial position from maximum density point.  The density reaches a maximum of $10^6$ times mean density at $r \approx 10^{-3}$ pc and decline to approximately mean density at $r\approx 3$ pc.  The three straight solid lines are $r^{-3/2}$, $r^{-2}$, and $r^{-5/2}$ power laws. \label{fig:good_rho_example}}
\end{figure*}

@@

What plots should we show?
-velocities vs r
-angular momentum vs r
-mass vs r
-mdot vs r

In Figure \ref{fig:vr_example}, we plot $v_r$ (blue line) and $v_{\rm rms}$ (green line) as a function of $r$.  In the left panel, the radial velocity curve is sporadic, but the general trend is that $v_r$ declines in toward $0.1$ pc, but then rises inward of this point.  Plotted in red is a $r^{-1/2}$ power law and this inward rise appears to follow this general trend.  The turbulent velocity is smoother, but it follows the general trend of the $v_r$ curve in that it falls slowly inward toward $]\approx 0.1 $ pc before rising inward of that, roughly tracking the $r^{-1/2}$ power law.  These general trends are in rough agreement with our analytic expectations.

{\bf DISCUSS RIGHT PANEL}

\begin{figure*}
\plottwo{Track_0256_000_vr.png}{Track_0132_000_vr.png}
\caption{Radial velocity, $v_r$ (blue line), and turbulent velocity, $v_{\rm rms}$ (green line) as a function of radial position from maximum density point.  A $r^{-1/2}$ power law is shown as a red line. \label{fig:vr_example}}
\end{figure*}

A hint of why these different behaviors emerge from looking at the $M(r)$.  In Figure \ref{fig:mass_example}, we plot the mass as a function of radius.  Regions where $M(r)$ flattens implies that the mass in this region can be treated using a point mass approximation.  Here it is apparent that the regions that can be treated a point mass corresponds to regions in where the density follows a $r^{-3/2}$ power law and the radial and turbulent velocities follow a $r^{-1/2}$ power law.

\begin{figure*}
\plottwo{Track_0256_000_mass.png}{Track_0132_000_mass.png}
\caption{WRITE CAPTION: Radial velocity, $v_r$ (blue line), and turbulent velocity, $v_{\rm rms}$ (green line) as a function of radial position from maximum density point.  A $r^{-1/2}$ power law is shown as a red line. \label{fig:mass_example}}
\end{figure*}
